---
title: "Amtrak Summary"
output: 
  html_document:
    theme: cerulean
    toc: true
    number_sections: true
    toc_depth: 2
    toc_float: 
      collapsed: true
      smooth_scroll: false
---
***
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      cache = TRUE, 
                      results = "hide", 
                      warning = FALSE)
```

# Methodology
***
## R Specific Packages Used
***
```{r echo=TRUE, warning = FALSE, message = FALSE}
#package install and load~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
library(data.table)
library(magrittr)
library(dplyr)
library(stringr)
library(lubridate)
library(kableExtra)
library(knitr)
library(ggplot2)
library(forcats)
library(visdat)
```

## Data Import 
***
```{r}
#package install and load~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

#defining asset data columns~~~~~
names_indx = c('assetspecid', 'assetnum', 'assetattrid', 
               'classstructureid', 'displaysequence', 'alnvalue', 
               'changedate', 'changeby',  'Data_Date')

#loading asset data~~~~~
asset = fread("./data/ASSETSPEC 2020-03-16.csv") %>% 
  set_colnames(names_indx) 

#munging asset data~~~~~
index = grepl("SEDTRACKSEGMENT", asset$assetattrid) | 
  grepl("SED_CULVERTSPAN_", asset$assetattrid) |
  grepl("AMTMAX", asset$assetattrid) |
  grepl("JCH", asset$assetattrid) == TRUE

asset_records_removed = asset[index,]  

asset_records_removed %>% 
  fwrite(file = "./output/data/asset_records_removed.csv")

asset = asset[!index,]
```

The data used for this report was `ASSETSPEC 2020-03-16.csv`, it is referred to as ASSETSPEC in this document

The number of records in ASSETSPEC is **`r nrow(asset)`**. 

## Data Filtering
***
The loaded ASSETSPEC was filtered to exclude the following items : *SEDTRACKSEGMENT%*, *SED_CULVERTSPAN_%*, *AMTMAX%*, and *%JCH%*.  
The first two items were removed because their assetattrids values did not match those in the source files.   
In particular, they include the name of the parent source file in each assetattrid making it very difficult to properly join with the source files.   

In total, **`r nrow(asset_records_removed)`** were removed from ASSETSPEC during the filtering.  
A plot of the removed records per filtered item can be seen below.  

```{r results='asis', fig.height=4, fig.width=6, fig.align='left'}
asset_records_removed[str_detect(assetattrid, "SEDTRACKSEGMENT")]$assetattrid = "SEDTRACKSEGMENT" 
asset_records_removed[str_detect(assetattrid, "SED_CULVERTSPAN")]$assetattrid = "SED_CULVERTSPAN" 
asset_records_removed[str_detect(assetattrid, "AMTMAX")]$assetattrid = "AMTMAX" 
asset_records_removed[str_detect(assetattrid, "JCH")]$assetattrid = "JCH" 

asset_records_removed %>%  
  .[,.(.N), by = .(assetattrid)] %>% 
  .[,`:=`(assetattrid = fct_reorder(assetattrid, N, max))] %>% 
  ggplot() + 
  geom_col(aes(assetattrid, N), fill = "light blue") + 
  geom_label(aes(assetattrid, N, label = N)) +
  ylim(c(0,1280000)) +
  coord_flip() +
  labs(x = "", y = "Count", title = "Number of records removed by filtered assetattrid") +
  theme_classic()  
```
   
A small selection of these records can be seen below as an example.    
These items were written out as a csv file titled *asset_records_removed.csv*.    
    
```{r results='asis'}
asset_records_removed %>% 
  sample_n(100) %>%  
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = T, font_size = 11) %>%
  scroll_box(height = "200px")
```

```{r}
#loading source file information data~~~~~
master_id = fread("./data/master_id.csv")
master_id_lookup = fread("./data/master_id_lookup.csv") %>%  
  .[,`:=`(full_src = paste0("./data/", src, ".csv"))]
  

#removing unnneded source file directories
index = grepl("GEO", master_id_lookup$src) | grepl("Speed", master_id_lookup$src) == TRUE
master_id_lookup = master_id_lookup[!index,]

#merging both files and changing attribute data type
all_source_file_ids = master_id %>%
  merge(master_id_lookup) %>% 
  .[,c(2:3)] %>%  
  unique()

all_source_file_ids$ID = all_source_file_ids$ID %>%  as.integer()
```

```{r}
#ASSETSPEC side EDA and munging~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

#ASSETSPEC record with SED_ID~~~~~
#NA/NULLs cleaned
lookup_asset_num_id = asset[assetattrid == "SED_ID",c(1,2,3,6)] %>% 
  .[order(alnvalue)]

lookup_asset_num_id$alnvalue = lookup_asset_num_id$alnvalue %>%  
  as.integer()

#Record with duplcicated SED_IDs
lookup_asset_num_id_duplicated = lookup_asset_num_id[duplicated(lookup_asset_num_id)] 
  unique

#Non_Empty SED_IDs from Asset
lookup_asset_num_id_nonempty = lookup_asset_num_id[!is.na(alnvalue),] %>% unique()

#Empty SED_IDs from Asset
lookup_asset_num_id_NA = lookup_asset_num_id[is.na(alnvalue),] %>% unique()
# lookup_asset_num_id_NA = lookup_asset_num_id[alnvalue == "NULL",] %>% unique()

#full asset table given Empty SED_IDs from Asset
#USED AS REFERNCE CAN BE EXPORTED IF NEEDED
asset_num_id_NA = semi_join(asset, lookup_asset_num_id_NA, by = c("assetnum")) %>% 
  arrange(-desc(assetnum), assetattrid)
```

## Extracting IDs from ASSETSPEC
***
The total number of records where assetattrid == SED_ID was **`r nrow(lookup_asset_num_id)`**.  
The total number of these records which have NA alnvalues was  **`r nrow(lookup_asset_num_id_NA)`**.   
These were removed from the rest of the analysis.   
In total, **`r nrow(lookup_asset_num_id_nonempty)`** unique SED_ID records were in the ASSETSPEC data.      

```{r}
#section~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#merges all relevant source SED extract IDs with nonempty asset IDS
raw_merge = all_source_file_ids %>% 
  merge(., 
        lookup_asset_num_id_nonempty, 
        by.x = "ID", 
        by.y = "alnvalue", 
        all = TRUE) %>% 
  data.table() %>% 
  unique()
```

```{r}
#full merge check and identification of NA records
merge_check_NA = raw_merge[!complete.cases(raw_merge)] #all rows w/ NA
merge_check_NA_num_total = merge_check_NA %>%  nrow()

# merge_check_NA %>%  
  # visdat::vis_dat(sort_type =  FALSE)

merge_check_NA_src = merge_check_NA[is.na(src)] #records w/ asset data but no s.file date
merge_check_NA_src_num = merge_check_NA_src %>%  nrow()

merge_check_NA_assetnum = merge_check_NA[is.na(assetnum)] #records w/ s.file date but no asset data
merge_check_NA_assetnum_num = merge_check_NA_assetnum %>%  nrow()

# raw_merge %>%  
  # visdat::vis_dat(sort_type =  FALSE)
```


```{r}
#matched IDs b/w SEDEXTARCT and ASSETSPEC 
#complete cases
master_matched_ids = raw_merge %>%  
  na.omit() %>%  
  unique()

duplicated_id_list = master_matched_ids[duplicated(ID),1] %>%  
  unique()

duplicated_record_list = master_matched_ids[duplicated(master_matched_ids),]

master_matched_ids_duplicate_rm = anti_join(master_matched_ids,
                                            duplicated_id_list,
                                            by = "ID") %>%
  data.table() %>%
  .[order(ID), c(1:4)]

#THIS IS IMPORTANT SHOULD THEY BE REMOVED??? THEY ARE CURRENTLY NOT
master_matched_ids_duplicate_only = semi_join(master_matched_ids,
                                              duplicated_id_list,
                                              by = "ID") %>%
  data.table() %>%
  .[order(ID),] 


```

These records were matched against a lookup table which contained all source file names and the IDs of their records.   
This was done to match each unique *SED_ID* in ASSETSPEC to it's respective source file.     
In total, there were **`r nrow(master_matched_ids)`** matches.    

```{r}
#section~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#DT below has all records ASSETNUMS where their SED_ID values were found
asset_merged = lookup_asset_num_id_nonempty %>%  
  semi_join(asset[,c(1,2,3,6)], ., by = c("assetnum")) %>% 
  merge(., master_matched_ids[,c(-3,-5)], by = c("assetnum")) %>% 
  data.table() %>% 
  unique()

asset_merged$ID = as.integer(asset_merged$ID)

#full merge check and identification of NA records
merge_check_NA = asset_merged[!complete.cases(asset_merged)] #all rows w/ NA
merge_check_NA_num_total = merge_check_NA %>%  nrow()
# merge_check_NA %>%  
  # visdat::vis_dat()


```

All records with matching assetnum values corresponding to the *SED_ID* records were extracted from ASSETSPEC. In total, there were **`r nrow(asset_merged)`** records extracted from ASSETSPEC. These records would be then matched against the corresponding source files attribute values.

```{r}
#removing SED_TUNNEL, has bad headers
index = grepl("Tunnel", asset_merged$src)
asset_merged = asset_merged[!index,]

index = grepl("ALTVER", asset_merged$src)
asset_merged = asset_merged[!index,]

#Extracting all matched ASSETxSEDEXTRACT records' columns and values
suppressMessages({ 
  suppressWarnings({
    
    retreived_source_id_info = data.table()
    
    print("Extracting data from the following source files:")
    for (i in unique(asset_merged$src)){
      
      print(i)

      tmp = asset_merged %>% 
        .[src == i,ID] %>%  
        unique()

      retreived_source_id_info = master_id_lookup[src == i,full_src] %>%
        fread(., colClasses = 'character') %>% 
        .[ID %in% tmp,] %>% 
        .[,`:=`(id = ID)] %>%  
        purrr::map_df(as.character) %>% 
        reshape2::melt(id.vars = c("ID"), 
                       variable.factor = FALSE, 
                       warning = FALSE) %>% 
        data.table() %>% 
        .[,`:=`(assetattrid = paste0("SED_", str_to_upper(variable)))] %>%  
        bind_rows(retreived_source_id_info, .)
    }
    print("Done")
  })
})

retreived_source_id_info$ID = retreived_source_id_info$ID %>%  
  as.integer()

```


```{r results='asis', fig.height=4, fig.width=6, fig.align='left'}
#full merge check and identification of NA records
merge_check_NA = retreived_source_id_info[!complete.cases(retreived_source_id_info)] #all rows w/ NA
merge_check_NA_num_total = merge_check_NA %>%  nrow()

# merge_check_NA %>%  
  # visdat::vis_dat(sort_type =  FALSE)

```


```{r}
# retreived_source_id_info[value == ""]$value = "NULL"
```

## Source File Attributes
***
All matched SED_IDs' attribute data were then extracted from the source files.   
In total, this extraction resulted in **`r nrow(retreived_source_id_info)`** records.   
Each record in this table represents an attribute for a particular matched *SED_ID* value.   
This table was then joined with all the extracted records from ASSETSPEC on the record's *SED_ID* and *assetattrid*. 

# Initial ASSETSEPC & Extract Merge
***
```{r}
#section~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#investigating mismatched occurance
colum_order_index = c("src", "assetnum", "ID", "assetspecid", 
                      "assetattrid", "variable", "alnvalue", "value")

attribute_value_master = merge(asset_merged, 
                               retreived_source_id_info, 
                               by.x = c("ID", "assetattrid"), 
                               by.y = c("ID", "assetattrid"), all = TRUE) %>%  
  unique() %>% 
  .[,..colum_order_index] %>%
  .[order(src, ID, assetnum, assetattrid,)] %>% 
  .[,-1] %>%  
  merge(., all_source_file_ids, by = "ID" ) %>% 
  .[,..colum_order_index] %>%  
  .[order(src, ID, assetnum, assetattrid,)]

index = grepl("JCH", attribute_value_master$assetattrid) 
attribute_value_master = attribute_value_master[!index]

attribute_value_master_rows = attribute_value_master %>%  nrow()
```

## Summary
***
The raw merge of these two tables resulted in **`r nrow(attribute_value_master)`** records. 
The table's columns are:   

* src -> the source file associated with the SED_ID
* assetnum -> the assetnum associated with 
* ID -> the SED_ID for that record
* assetattrid -> the attribute name from the ASSETSPEC table
* variable -> the attribute name from the source files
* alnvalue -> the value associated with the attribute from the ASSETSPEC table
* value -> the value associated with the attribute from the source files

## Missing (NA) Data from Merge
***
```{r}
merge_check_NA = attribute_value_master[!complete.cases(attribute_value_master)] #all rows w/ NA
merge_check_NA_num_total = merge_check_NA %>%  nrow()

na_count = is.na(merge_check_NA) %>%  
  data.table() %>% 
  .[,.(.N), by = .(src, ID, assetnum, assetspecid, assetattrid, alnvalue, variable, value)] %>% 
  .[,-c('src', 'ID', 'assetattrid')] 

```

A large number of records from the data merge were populated with NAs.
Number NA records: **`r  nrow(merge_check_NA)`**.    
That is roughly **`r  100*round(nrow(merge_check_NA)/nrow(attribute_value_master), 3)`** percent of the resulting data mereger.  
NAs occure when data is missing.   
It is important to track the number of missing values and the patterns they occur in as it indicates points where either source cannot map to the other.   
Examples of potential causes include:
     
* Outright data transfer failure - eg. source 1 contains data source 2 does not, or visa versa
* Data compeltely mismatched - eg. attribute names are different between data sets   

As an aside, NAs are different than a *NULL* values.   
The latter is not considered missing data as it is a litteral data value that can be referenced with.  
     
The plot below depicts the total number of incomplete/NA records and the prevailing patterns in which the NAs occured. 

```{r results='asis', fig.height=4, fig.width=6, fig.align='left'}
#full merge check and identification of NA record
missing_data_viz = merge_check_NA %>%  
  .[,.(src, ID, assetnum, assetspecid, assetattrid, alnvalue, variable, value)] %>%  
  .[order(assetnum)] %>% 
  vis_dat(warn_large_data = FALSE, 
          sort_type = FALSE)

missing_data_viz
```

The table below details the NA type pattern, the number of occurances, and an emblematic example of record with said NA type (record examples start at column **assetnum** to **value**.    
       
* **Row 1**:    
  + Instances where ASSETSPEC data were missing while source file data were present. 
  + Potential Cause: Not all data was tranferred to ASSETSPEC
* **Row 2**:
  + Instances where ASSETSPEC data were present while source file data were missing 
  + Potential Cause: assetattrids don' map between data sets 
    - ASSETSPEC assetattrid changed in transfer 
    - Source file attribute names were doubled up
* **Row 3**:
  + Data set attributes map between data sets, both values don't exist 
    - Could be considered a positive match between values
* **Row 4**:
  + Source file value is missing while corresponding value is present 
  + Very strange but very low count

```{r results='asis'}

ffmerge_na_no_asset_data =  merge_check_NA[is.na(assetnum) &
                 is.na(assetspecid) &
                 is.na(alnvalue) &
                 !is.na(variable) &
                 !is.na(value),]
                 
ffmerge_na_no_alnvalue_value = merge_check_NA[!is.na(assetnum) &
                 !is.na(assetspecid) &
                 is.na(alnvalue) &
                 !is.na(variable) &
                 is.na(value),]

ffmerge_na_no_extract_data = merge_check_NA[!is.na(assetnum) &
                 !is.na(assetspecid) &
                 !is.na(alnvalue) &
                 is.na(variable) &
                 is.na(value),]

ffmerge_na_no_value = merge_check_NA[!is.na(assetnum) &
                 !is.na(assetspecid) &
                 !is.na(alnvalue) &
                 !is.na(variable) &
                 is.na(value),]

ffmerge_summary_table = bind_cols(data.table(na_type = c('no_asset_data', 
                                 'no_extract_data', 
                                 'no_alnvalue_value',
                                 'no_value'), 
                     na_count = na_count$N),
          bind_rows(ffmerge_na_no_asset_data[1,], 
                    ffmerge_na_no_extract_data[1,],
                    ffmerge_na_no_alnvalue_value[1,],
                    ffmerge_na_no_value[1,]) %>%  
            .[,.(src, ID, assetnum, assetspecid, assetattrid, alnvalue, variable, value)]) 

ffmerge_summary_table %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = T, font_size = 11) %>%
  scroll_box(height = "200px", width = "100%") 
```

```{r}
#I dont want to do this, we want to keep NULLS that are native there and get rid of NAs after cataloging them

#fixes NULLs, NAs, Empties
# attribute_value_master[is.na(variable)]$variable = "NULL"
# attribute_value_master[variable == ""]$variable = "NULL"
# attribute_value_master[is.na(value)]$value = "NULL"
# attribute_value_master[value == ""]$value = "NULL"
# attribute_value_master[is.na(alnvalue)]$alnvalue = "NULL"
# attribute_value_master[assetnum == ""]$assetnum = "NULL"
# attribute_value_master[is.na(assetnum)]$assetnum = "NULL"
# attribute_value_master[src == ""]$src = "NULL"
# attribute_value_master[is.na(src)]$src = "NULL"
# attribute_value_master[assetspecid == ""]$assetspecid = "NULL"
# attribute_value_master[is.na(assetspecid)]$assetspecid = "NULL"
# attribute_value_master[assetspecid == "NA"]$assetspecid = "NULL"
# 
# attribute_value_master_rows = nrow(attribute_value_master)
```

```{r results='asis'}
#redundent 

# no_sfile_attribute = attribute_value_master %>% .[variable  == "NULL", ] 
# no_sfile_attribute_nrows = nrow(no_sfile_attribute)`
# 
# no_assetattrid_attribute = attribute_value_master %>% .[assetattrid  == "NULL", ] 
# no_assetattrid_attribute_nrows = nrow(no_assetattrid_attribute)
# 
# no_attribute_transfer_src_failure = attribute_value_master %>% .[src  == "NULL", ] 
# no_attribute_transfer_src_failure_rows = nrow(no_attribute_transfer_src_failure)
```

```{r}
attribute_value_master = attribute_value_master %>%  
  na.omit()

attribute_value_master_good_row = attribute_value_master %>%  nrow()
```

These records were ultimately removed from the merged table, resulting in `r nrow(attribute_value_master_good_row)` non-NA records.   
This table only contains compelete reocrds.  

```{r}
#matching columns but 
attribute_value_notmatching =  attribute_value_master %>% 
  .[alnvalue != value,] %>% 
  .[,..colum_order_index] %>%  
  .[order(src, ID, assetnum, assetattrid,)]

attribute_value_matching = attribute_value_master %>% 
  .[alnvalue == value,] %>% 
  .[,..colum_order_index] %>%  
  .[order(src, ID, assetnum, assetattrid,)]
```

After the removal of these records, there were **`r nrow(attribute_value_notmatching)`** failed matches and **`r nrow(attribute_value_matching)`** positive matches.  


## False Mismatch Removal
***
After perfroming spot checks, it was found that there were a substantial number of false positive *alnvalue/value* mismatches.    
These mismatches were caused by a number of things, ranging from simple CASE or white space padding issues to more critical character encoding errors.     
In either instance, these mismatches were deemed to be falsely attributed to the record transfer and records where this occurred were removed from the mismatch record table.    

Some examples of this will be listed below:   

### Case and Whitespace
***
```{r results='asis'}
#removes all mismatch cases caused by CASE or whitespace issues
index_character_mismatch = str_trim(str_to_lower(attribute_value_notmatching$alnvalue), side = "both") == str_trim(str_to_lower(attribute_value_notmatching$value),side = "both")
tmp = attribute_value_notmatching[!index_character_mismatch]
attribute_value_notmatching[index_character_mismatch] %>% 
  fwrite(file = "./output/data/total_matched_example_case_whitespace_sensitive.csv")

attribute_value_notmatching[index_character_mismatch] %>% 
  sample_n(5) %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = T, font_size = 11) %>%
  scroll_box(height = "200px") 
```

### Numeric Padding
***
```{r results='asis'}
#removes all records where mismatch was caused by false padding encoding
index_alnvalue = as.numeric(tmp$alnvalue)
index_alnvalue[is.na(index_alnvalue)] = 0

index_value = as.numeric(tmp$value)
index_value[is.na(index_value)] = -29348576.127

index_PADDING_mismatch = index_alnvalue == index_value

tmp[index_PADDING_mismatch] %>% 
  fwrite(file = "./output/data/total_matched_example_padding.csv")

tmp[index_PADDING_mismatch] %>% 
  sample_n(5) %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = T, font_size = 11) %>%
  scroll_box(height = "200px") 

tmp = tmp[!index_PADDING_mismatch] 
```

### Rounding
***
```{r results='asis'}
#removes long/lat columns as proven to be just a rounding error
index = grepl("LONG", tmp$assetattrid) | grepl("LATITUDE", tmp$assetattrid)
tmp[index] %>% 
  fwrite(file = "./output/data/total_matched_example_rounding.csv")

tmp[index] %>% 
  sample_n(5) %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = T, font_size = 11)

tmp = tmp[!index]
```

### Special Characters
***
```{r results='asis'}
#removes all records where mismatch was caused by false encoding
index_DIMENSIONS = tmp$assetattrid == "SED_DIMENSIONS"

total_matched_bad = tmp[!index_DIMENSIONS] 

tmp[index_DIMENSIONS]  %>% 
  fwrite(file = "./output/data/total_matched_example_seddimensions.csv")

tmp[index_DIMENSIONS] %>% 
  sample_n(5) %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = T, font_size = 11) %>%
  scroll_box(height = "200px") 
``` 

### Date Format Mismatch 
***
```{r results='asis'}
index_DATE_ENCODE_errors = total_matched_bad[assetattrid == 'SED_DATEVERIFIED' | 
                              assetattrid == 'SED_INSTALLDATE', ]$alnvalue %>% 
  str_length() > 7

total_matched_bad[assetattrid == 'SED_DATEVERIFIED' | 
                    assetattrid == 'SED_INSTALLDATE', ][!index_DATE_ENCODE_errors] %>%
  fwrite(file = "./output/data/total_matched_example_gooddates.csv")

tmp_good_date = total_matched_bad[assetattrid == 'SED_DATEVERIFIED' | 
                    assetattrid == 'SED_INSTALLDATE', ][index_DATE_ENCODE_errors]

tmp_good_date %>% 
  sample_n(5) %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = T, font_size = 11) %>%
  scroll_box(height = "200px") 
```

```{r}
total_matched_bad = anti_join(total_matched_bad,
                              tmp_good_date, 
                              by = colum_order_index) %>%  
  data.table()

total_matched_good = attribute_value_master %>%  
  anti_join(total_matched_bad, by = c('assetnum', 'assetspecid', "assetattrid")) %>%  
  data.table()

total_matched_bad %>%  
  fwrite(file = "./output/data/total_matched_bad.csv")

total_matched_good %>%  
  fwrite(file = "./output/data/total_matched_good.csv")
```

```{r}
#DELETE< INVESTIGATION ONLY
total_matched_bad %>%  
  .[ID == '506697' &	
      assetspecid == '6452016',value] 

attribute_value_master
attribute_value_master[value == ""]
```




# Final ASSETSEPC & Extract Merge 
***
## Summary
***
**`r nrow(total_matched_good)`** records were properly matched on the *alnvalue* and *value* coulmns.        
Examples of these records can are below:   
    
```{r results="asis"}
total_matched_good %>% 
  sample_n(500) %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = T, font_size = 11) %>%
  scroll_box( height = "200px")
```
   
*CAUTION: Some values may appear to be non-matching, this is likely due to an encoding error produced by R. Most of these types of mismatches are accounted for and are addressed below.  

The number of false matched records is **`r nrow(total_matched_bad)`**. Examples of these records can are below:   
```{r results="asis"}
total_matched_bad %>%
  sample_n(500) %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = T, font_size = 11) %>%
  scroll_box(height = "200px") 
```

The match failure rate is roughly **`r 100*nrow(total_matched_bad)/(nrow(total_matched_bad)+ nrow(total_matched_good))`** percent.

## Failed Match Diagnostics
***

### Total Records   
The table below details:    
      
* The source file where the matched ID record came from
* Total matches - where IDs and *assetattrids* metched between the source files and ASSETSPEC 
* Number of postive matches - where the alnvalue and value matched or were deemed a 'match' by manual inspection
* Failed matches
* Failure rate in percent

The table indicates where most of the failures originated from and where effort should be placed to buy down match errors.

```{r results="asis"}
summary_diagnostic = total_matched_bad %>%  
  .[,.(fail = .N), by = .(src)] %>%  
  merge(total_matched_good %>%  
          .[,.(pass = .N), by = .(src)], on = "src") %>%  
  .[,`:=`(total = fail + pass)] %>% 
  .[,`:=`(fail_per = 100*round(fail/total,3))] %>%  
  .[order(-fail)] 

summary_diagnostic %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = T, font_size = 11) %>%
  scroll_box( height = "200px") 
```


### Null values kept   
***
The two tree plots below give an indication to the scope and scale of mismatched values.       
The top plot indicates mismatched records by source file and the bottom plot by *assetattid*.  
They report all mismatches between *alnvalue* and *value* regadless if **NULL** isa present in either.  

```{r results='asis', fig.height=4, fig.width=8, fig.align='left'}

summary_diagnostic %>%  
  .[,`:=`(src = str_remove(src, "SED_"))] %>%
  treemap::treemap(., 
                 index = "src", 
                 vSize = "fail", 
                 vColor = "fail_per",
                 type = "value", 
                 title = "Failed matches per originating source file")
```

```{r}
summary_diagnostic = total_matched_bad %>%  
  .[,.(fail = .N), by = .(assetattrid)] %>%  
  merge(total_matched_good %>%  
          .[,.(pass = .N), by = .(assetattrid)], on = "assetattrid") %>%  
  .[,`:=`(total = fail + pass)] %>% 
  .[,`:=`(fail_per = 100*round(fail/total,3))] %>%  
  .[order(-fail)] %>%  
  .[,`:=`(assetattrid = str_remove(assetattrid, "SED_"))]
```

```{r results='asis', fig.height=4, fig.width=8, fig.align='left'}
treemap::treemap(summary_diagnostic, 
                 index = "assetattrid", 
                 vSize = "fail", 
                 vColor = "fail_per",
                 type = "value", 
                 title = "Failed matches per assetattributeid")
```

### Null Values Removed 
***
The plots below display the same data as above but with all records containing **NULL** in either *alnvalue* or *value* removed.   
These should be used in direct comparison with the plots above
These are TRUE mismatch cases where there were reported values for each matched ID attribute in both datasets but were wrond for some reason.  
      
```{r results="asis"}
#poor match metrics~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
total_matched_bad_non_null = total_matched_bad[alnvalue != "NULL" &  value != "NULL"]
total_matched_bad_non_null %>%  
  fwrite(file = "./output/data/total_matched_bad_non_null.csv")

total_matched_bad_null_value = total_matched_bad[value == "NULL"]
total_matched_bad_null_value %>%  
  fwrite(file = "./output/data/total_matched_bad_null_value.csv")

total_matched_bad_null_alnvalue = total_matched_bad[alnvalue == "NULL"] 
total_matched_bad_null_alnvalue %>%  
  fwrite(file = "./output/data/total_matched_bad_null_alnvalue.csv")
```

```{r results="asis"}
summary_diagnostic = total_matched_bad_non_null %>%  
  .[,.(fail = .N), by = .(src)] %>%  
  .[,`:=`(src = str_remove(src, "SED_"))]
  
```

```{r results='asis', fig.height=4, fig.width=8, fig.align='left'}
treemap::treemap(summary_diagnostic, 
                 index = "src", 
                 vSize = "fail", 
                 vColor = "fail",
                 type = "value", 
                 title = "Failed matches per originating source file, NULL reocrds removed")
```

```{r}
summary_diagnostic = total_matched_bad %>%  
  .[,.(fail = .N), by = .(assetattrid)] %>%  
  .[,`:=`(assetattrid = str_remove(assetattrid, "SED_"))] 
```

```{r results='asis', fig.height=4, fig.width=8, fig.align='left'}
treemap::treemap(summary_diagnostic, 
                 index = "assetattrid", 
                 vSize = "fail", 
                 vColor = "fail",
                 type = "value", 
                 title = "Failed matches per assetattributeid, NULL reocrds removed")
```
  
**`r nrow(total_matched_bad_non_null)`** mismatches occurred when neither alnvalue or value were NULL.   
These cases are of the most concern as they are legitimate mismatch errors. 
The records per source and assetattrid can be seen below:
```{r results="asis"}
total_matched_bad_non_null %>% 
  .[,.(.N), by = .(src, assetattrid)] %>%  
  .[order(-N)] %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = T, font_size = 11) %>%
  scroll_box(height = "200px")  
```
**`r nrow(total_matched_bad_null_value)`** mismatches occurred when alnvalue was non-NULL and value was NULL.   
The records per source and assetattrid can be seen below:  
        
```{r results="asis"}
total_matched_bad_null_value %>% 
  .[,.(.N), by = .(src, assetattrid)] %>%  
  .[order(-N)] %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = T, font_size = 11) %>%
  scroll_box(height = "200px") 
```

**`r nrow(total_matched_bad_null_alnvalue)`** mismatches occurred when alnvalue was NULL and value was non-NULL.   
The records per source and assetattrid can be seen below:    
   
```{r results="asis"}
total_matched_bad_null_alnvalue %>% 
  .[,.(.N), by = .(src, assetattrid)] %>%  
  .[order(-N)] %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = T, font_size = 11) %>%
  scroll_box(height = "200px")  
```

## Match Error Investigation
***

### Missing attributes in ASSETSPEC
***
This is a big problem and needs to be fixed.
   
Fixes/comments:
   
* Consistent attribute naming in the source files
* Flagging source file attribute names when we know they are going to be changed in ASSETSPEC
* Some ability to make the mapping better between changed attributeids
    
```{r results = "asis"}
# no_sfile_attribute %>%
#   sample_n(5) %>% 
#   kable() %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = T, font_size = 11)
```

### Date Errors
***
```{r results = "asis"}
####dates in the format, not UNIX what is it
index = grepl("DATE", total_matched_bad$assetattrid)
```

As seen in the above plot, a bulk of the valid record mismatches are from the *DATE* attributes.

There are **`r nrow(total_matched_bad[index, c(1,5,7,8)] )`** records where a *DATE* related attribute caused a mismatched record. 
  
Fixes/comments:
  
* Mismatch error caused by the ASSETSPEC alnvalues being formatted as a #### numeric
* this is not UNIX or some common time format
* They need to be reformatted to %d/%m/%Y format
   
```{r results = "asis"}
total_matched_bad[index, c(1,5,7,8)] %>% 
  unique() %>% 
  sample_n(5) %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = T, font_size = 11)
```


### Special character formatting
***
The SED_Dimensions assetattidid used unconventional formatting for dimensions. 
   
Fixes/comments:   
      
* Uses single and double quotes to indicate feet or inches presumably
* This is bad practice ideally be parsed into separate length and width components.
* Reported units are also inconsistent, and should be either all in feet or inches.
    
```{r results = "asis"}
attribute_value_notmatching[assetattrid == "SED_DIMENSIONS"] %>% 
  sample_n(5) %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = T, font_size = 11) 

yolo1 = nrow(total_matched_bad[value == ""])
yolo2 = nrow(total_matched_bad[alnvalue == ""])
```

### Empty Values
***
Empty character values are being recorded only for the source file data values.  
After the source file and ASSETSPEC merge and removal of incomplete/NA records, there were:   
      
* **`r yolo1`** records where this occurs in the source file data
* **`r yolo2`** records where this occurs in the ASSETSPEC data

This match error is substantial as it accoutns for roughly **`r 100*round(yolo1/nrow(total_matched_bad),3)`** percent of the **`r nrow(total_matched_bad)`** total bad matches.
   
Fixes/comments:   
      
* Attributes properly map between data sets
* Spot checks reveal that attribute exists in source files but with an empty cell
* Empty cell in ASSETSPEC are reflected as NULL, in theory no-mismatch occuring
  + Can ignore these 
  + Or force empty cells to be NULL in source files

Table detailing orginating source files and correspoinging alnvalue:
```{r results = "asis"}
total_matched_bad[value == ""] %>% 
  .[,.(.N), by = .(src, alnvalue)] %>% 
  .[order(-N)] %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = T, font_size = 11) %>%
  scroll_box(height = "200px")
```

Example of records:
```{r results = "asis"}
attribute_value_master[value == ""] %>%   
  sample_n(5) %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = T, font_size = 11)  
```

# Richter Summary 
***
1) **From the total number of ASSETSPEC records, how many ASSETSPEC records are excluded and why?**        
The loaded ASSETSPEC was filtered to exclude the following items:    
*SEDTRACKSEGMENT%*, *SED_CULVERTSPAN_%*, *AMTMAX%*, and *%JCH%*.        
**`r nrow(asset)-nrow(asset_records_removed)`** OK, **`r nrow(asset_records_removed)`** NOT, (=Total **`r nrow(asset)`**)  

2) **Out of the total number of SED_ID values in ASSETSPEC, how many match the extract data?**    
Number of records where assetattrid == SED_ID is **`r nrow(lookup_asset_num_id_nonempty)`**.   
The total number of these records which have NULL alnvalues was  **`r nrow(lookup_asset_num_id_NA)`**.    
These were removed from the rest of the analysis.    
In total, there were **`r nrow(master_matched_ids)`** matches where assetattrid == SED_ID.   

3) **For every datapoint in the extract dataset that belongs to SED_IDs that are matched, how many of these have matching entries in the assetspec dataset (col name = assetattrid)?**    
Complete Records: **`r attribute_value_master_good_row`**.     
Incomplete Records: **`r sum(ffmerge_summary_table$na_count)`**.  

* IR.1: **`r ffmerge_summary_table$na_count[1]`** -> no assetattrid value (ASSETSPEC side)     
* IR.2: **`r ffmerge_summary_table$na_count[2]`** -> no variable value (source file side)    
* IR.3: **`r ffmerge_summary_table$na_count[3]`** -> missing ASSETSPEC and sourve file data (attributes map)  
* IR.4: **`r ffmerge_summary_table$na_count[4]`** -> missing sourve file data (attributes map) 
Total Matches: **`r attribute_value_master_rows`** 

4) **For every matched entry, does the alnvalue = the sed value? How many match and how many do not match?**    
Good Matches: **`r nrow(total_matched_good)`**    
Bad Matches: **`r nrow(total_matched_bad)`**    
Total Matches: **`r nrow(total_matched_bad) + nrow(total_matched_good)`**      
Percent Failure: **`r 100*nrow(total_matched_bad)/(nrow(total_matched_bad)+ nrow(total_matched_good))`** percent.     
See following files for more detail:    
total_matched_good -> all good matches  
total_matched_bad -> all bad matches  
total_matched_bad_non_null.csv -> slice of bad matches, where neither data set values are null  
total_matched_bad_null_value.csv -> slice of bad matches, where source file values are null  
total_matched_bad_null_alnvalue.csv -> slice of bad matches, where ASSETSPEC values are null  
total_matched_bad_null_only.csv - poor match instances where source could not be found, possibly due to multiple IDs 









